---
title: "R Notebook"
output: html_notebook
---



data.frame':	4706 obs. of  46 variables:
 $ Provider.Number                                                                      : chr  "010001" "010005" "010006" "010007" ...
 $ Hospital.Name                                                                        : chr  "SOUTHEAST ALABAMA MEDICAL CENTER" "MARSHALL MEDICAL CENTER SOUTH" "ELIZA COFFEE MEMORIAL HOSPITAL" "MIZELL MEMORIAL HOSPITAL" ...
 $ Address.1                                                                            : chr  "1108 ROSS CLARK CIRCLE" "2505 U S HIGHWAY 431 NORTH" "205 MARENGO STREET" "702 N MAIN ST" ...
 $ Address.2                                                                            : chr  "" "" "" "" ...
 $ Address.3                                                                            : chr  "" "" "" "" ...
 $ City                                                                                 : chr  "DOTHAN" "BOAZ" "FLORENCE" "OPP" ...
 $ State                                                                                : chr  "AL" "AL" "AL" "AL" ...
 $ ZIP.Code                                                                             : chr  "36301" "35957" "35631" "36467" ...
 
 
 
 # Change type of Data.Table
 
```{r}
library("data.table")
install.packages('bit64')
library("bit64")

# Reading in data
outcome1 <- data.table::fread('outcome-of-care-measures.csv')
outcome[, (11) := lapply(.SD, as.numeric), .SDcols = (11)]
outcome[, lapply(.SD
                 , hist
                 , xlab= "Deaths"
                 , main = "Hospital 30-Day Death (Mortality) Rates from Heart Attack"
                 , col="lightblue")
        , .SDcols = (11)]
str(outcome)
names(outcome)
```
 
 
 
 
 #Temporary
 
```{r}
hospitalData <- data.table::fread('hospital-data.csv')
str(hospitalData)
```
 
 